Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-09-02 awipev-CO2.Rmd
revised months, vertical pH changes

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate( # create new variable depth
    depth = ifelse(
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 9, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                       date = d_hour$date,
                       month = month(d_hour$datetime))
```

@@

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(month))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

@@

p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs(x="T 11 m", y="T FB ", color = "Months") 
print(p) # p_temp_11_fb

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
print(p)

@@

```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, month,closest_datetime, at, sal_mix)

fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))

@@

p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_corr, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```

@@

#Per month
range <- d_all %>%
  dplyr::mutate(pH_range_more_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA)) %>%
  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
            pH_range_more_6m = max(pH_range_more_6m, na.rm = TRUE) - min(pH_range_more_6m, na.rm = TRUE),
            pH_range_more_9m = max(pHint_tot_sf_9m, na.rm = TRUE) - min(pHint_tot_sf_9m, na.rm = TRUE)) %>%
  ungroup()
print(kable(range, digits = 2))
```
The range is significantly larger during some months when the data deeper than 9 m are considered. It seems therefore better to stick pH_çm, that is pH deeper than 8 m.

@@

# RANGE of pH
range_dur <- tbl_df(
  d_all %>%
  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
  summarize(pH_range = max(ph_dur_corr) - min(ph_dur_corr))
)
quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)

# Per month
range_month <-
  range_dur %>%
  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))

size_point <- 0.4 # size of data points
p <-
  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(p) # plot_range_dur
```

@@

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
range_month <-
  d_all %>%
  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
  summarize(temp_mix_max = round( max(temp_mix, na.rm=TRUE), digits = 2),
            temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
            temp_ctd_1m_max = round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_1m_min = round(min(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_max = round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_min = round(min(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_max = round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_min = round(min(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_max = round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_min = round(min(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_max = round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_min = round(min(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_11m_max = round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
            temp_fb_min = round( min(temp_fb, na.rm=TRUE), digits = 2),
            sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
            sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
            sal_ctd_1m_max = round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_1m_min = round(min(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_max = round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_min = round(min(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_max = round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_min = round(min(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_max = round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_min = round(min(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_max = round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_min = round(min(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
            sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
            pH_sf_max = round(max(pHint_tot_sf_9m, na.rm=TRUE), digits = 4),
            pH_sf_min = round(min(pHint_tot_sf_9m, na.rm=TRUE), digits = 4))
kable(range_month, caption = "")
```

@@

fit <- lmodel2(data = d_all,  pHint_tot_sf_norm4 ~ pH_durafet_norm4 , nperm = 99)
pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = month))+
  geom_point( aes(color=factor(month)), size =1, alpha=0.5) + 
  facet_wrap( ~ factor(month), ncol = 3) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ #scale_colour_discrete(guide="none") +
  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Month ")  +theme_bw()

@@

p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = month)) +
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH durafet", y="pH spectro", color = "Months")
p
```

@@

p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = month)) +
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH seafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 1))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH spectro", y="pH seafet", color = "Months")
p
```

>>>>

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 9, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
```

@@

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

@@

p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs(x="T 11 m", y="T FB ", color = "Months") 
print(p) # p_temp_11_fb

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
print(p)

@@

```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, monthd,closest_datetime, at, sal_mix)

fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = monthd))+
  geom_text( aes(color=factor(monthd))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))

@@

p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_corr, label = monthd))+
   geom_text(aes(color = factor(monthd)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```

@@

#Per month
range <- d_all %>%
  dplyr::mutate(pH_range_more_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA)) %>%
  group_by(montht) %>%
  summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
            pH_range_more_6m = max(pH_range_more_6m, na.rm = TRUE) - min(pH_range_more_6m, na.rm = TRUE),
            pH_range_more_9m = max(pHint_tot_sf_9m, na.rm = TRUE) - min(pHint_tot_sf_9m, na.rm = TRUE)) %>%
  ungroup()
print(kable(range, digits = 2))

tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf, depth) %>%
  group_by(depth, montht) %>%
  ungroup()
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHT", x = "Depth (m)", y= "pHT") +
  facet_wrap(vars(montht), scale = "free_y")
print(p)

```
**Conclusion**:
The range is significantly larger during some months when the data deeper than 9 m are considered. Also, pH is sometimes higher at the surface, at other tilmes it is higher on the bottom (June). 
  + To compare with pCO2/pCO2 measured in the Ferryboxt seems therefore better to stick with pH_9m, that is at depths deeper than 8 m.
  + For air-sea CO2 fluxes

@@

# RANGE of pH
range_dur <- tbl_df(
  d_all %>%
  group_by(date, montht, year=year(datetime)) %>%
  summarize(pH_range = max(ph_dur_corr) - min(ph_dur_corr))
)
quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)

# Per month
range_month <-
  range_dur %>%
  group_by(montht) %>%
  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))

size_point <- 0.4 # size of data points
p <-
  ggplot(data=range_dur, aes(x = as.factor(montht), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(p) # plot_range_dur
```

@@

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
range_month <-
  d_all %>%
  group_by(montht) %>%
  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
  summarize(temp_mix_max = round( max(temp_mix, na.rm=TRUE), digits = 2),
            temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
            temp_ctd_1m_max = round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_1m_min = round(min(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_max = round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_3m_min = round(min(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_max = round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_5m_min = round(min(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_max = round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_7m_min = round(min(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_max = round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_ctd_9m_min = round(min(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            temp_11m_max = round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
            temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
            temp_fb_min = round( min(temp_fb, na.rm=TRUE), digits = 2),
            sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
            sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
            sal_ctd_1m_max = round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_1m_min = round(min(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_max = round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_3m_min = round(min(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_max = round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_5m_min = round(min(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_max = round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_7m_min = round(min(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_max = round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_ctd_9m_min = round(min(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
            sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
            sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
            pH_sf_max = round(max(pHint_tot_sf_9m, na.rm=TRUE), digits = 4),
            pH_sf_min = round(min(pHint_tot_sf_9m, na.rm=TRUE), digits = 4))
kable(range_month, caption = "")
```

@@

fit <- lmodel2(data = d_all,  pHint_tot_sf_norm4 ~ pH_durafet_norm4 , nperm = 99)
pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = monthd))+
  geom_point( aes(color=factor(monthd)), size =1, alpha=0.5) + 
  facet_wrap( ~ factor(monthd), ncol = 3) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ #scale_colour_discrete(guide="none") +
  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Month ")  +theme_bw()

@@

p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH durafet", y="pH spectro", color = "Months")
p
```

@@

p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH seafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 1))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH spectro", y="pH seafet", color = "Months")
p
```
